### 2020-12-04 paper/localpsf.tex
editing intro

% REQUIRED
\begin{abstract}
  We present an efficient matrix-free method for approximating locally translation invariant operators with locally supported non-negative integral kernels. The idea of the method is to compute impulse responses of the operator at a collection of well-spaced points, then interpolate these impulse responses to approximate impulse responses at other arbitrary points. We convert the resulting approximation to hierarchical matrix format, which allows us to perform matrix inversion or other matrix operations using fast hierarchical matrix arithmetic. Impulse responses are computed by applying the operator to a small number of Dirac comb ``batches'' of point sources, and special care is taken to ensure that the supports of the impulse responses within each batch do not overlap. We apply the method to approximate Hessians in large-scale PDE-constrained inverse problem with highly informative data. Numerical results demonstrate that our method substantially outperforms existing Hessian approximation methods which are based on low-rank approximation. Our method is able to form high quality approximations of high rank Hessians using only a small number of Hessian matrix-vector products.
%  Within each Dirac comb, the point sources must be spaced sufficiently far apart so that the impulse responses to those point sources do not overlap. We estimate the required spacing of point sources by applying the operator to a small number of constant, linear, and quadratic functions, then postprocessing the results.
\end{abstract}

@@

If $\mathcal{A}$ were translation invariant---i.e., if the exact equality $A(y+h, x+h) = A(y,x)$ held for arbitrary $x$, $y$, $h$---then it is straightforward to show that $\mathcal{A}$ would take the form of the convolution operator $\left(\mathcal{A}u\right)(v) = \left\langle v, \varphi_p \ast u\right\rangle_{L^2(\Omega)}$. Here $f \ast g$ denotes convolution of the functions $f$ and $g$. The convolution kernel,
\begin{equation*}
	\varphi_x(y) := A(y+x,x),
\end{equation*}
is the result of applying $\mathcal{A}$ to a point source at some fixed point $x$, then translating the resulting impulse response function re-center it at zero instead of $x$. Locally translation invariant operators act like convolution operators locally, but the convolution kernel, $\varphi_x$, varies as $x$ changes. We therefore sample $\varphi_{x_i}$ at a collection of points $\{x_i\}_{i=1}^r \subset \Omega$, and patch together the local convolution operators $u \mapsto \varphi_{x_i} \ast u$ using smooth weighting functions $w_i(x)$. This yields a product-convolution approximation, $\widetilde{\mathcal{A}} \approx \mathcal{A}$, given by
\begin{equation*}
	\left(\widetilde{\mathcal{A}}u\right)(v) := \left\langle v, \sum_{i=1}^r \varphi_{x_i} \ast \left(w_i \cdot u\right) \right\rangle_{L^2(\Omega)},
\end{equation*}
where $f \cdot g$ denotes pointwise multiplication of the functions $f$ and $g$.

@@

>>>>

% REQUIRED
\begin{abstract}
  We present an efficient matrix-free method for approximating locally translation invariant operators with locally supported non-negative integral kernels. The idea of the method is to compute impulse responses of the operator at a collection of well-spaced points, then interpolate these impulse responses to approximate impulse responses at other arbitrary points. We convert the resulting approximation to hierarchical matrix format, which allows us to perform matrix inversion or other matrix operations using fast hierarchical matrix arithmetic. Impulse responses are computed by applying the operator to a small number of Dirac comb ``batches'' of point sources, and special care is taken to ensure that the supports of the impulse responses within each batch do not overlap. We apply the method to approximate Hessians in large-scale PDE-constrained inverse problem with highly informative data. Numerical results demonstrate that our method substantially outperforms existing state-of-the-art Hessian approximation methods which are based on low-rank approximation. Our method is able to form high quality approximations of high rank Hessians using only a small number of Hessian matrix-vector products.
%  Within each Dirac comb, the point sources must be spaced sufficiently far apart so that the impulse responses to those point sources do not overlap. We estimate the required spacing of point sources by applying the operator to a small number of constant, linear, and quadratic functions, then postprocessing the results.
\end{abstract}

@@

If $\mathcal{A}$ were translation invariant (that is, if $A(y+h, x+h) = A(y,x)$ for all $x$, $y$, $h$) then it is straightforward to show that $\mathcal{A}$ would be a convolution operator, and the convolution kernel, $\varphi_x$, would be given by
\begin{equation}
\label{eq:convolution_kernel}
	\varphi_x(y) := A(y+x,x).
\end{equation}
The function $\varphi_x$ is the result of applying $\mathcal{A}$ to a point source at some fixed point $x$, then translating the resulting impulse response function re-center it at zero instead of $x$. Locally translation invariant operators act like convolution operators locally, but the convolution kernel, $\varphi_x$, varies as $x$ changes. Locally translation invariant operators may therefore be approximated by spatially varying weighted sums of convolution operators of the form
\begin{equation}
\label{eq:product_convolution}
	\left(\mathcal{A}u\right)(v) \approx \left(\widetilde{\mathcal{A}}u\right)(v) := \left\langle v, \sum_{i=1}^r \varphi_{x_i} \ast \left(w_i \cdot u\right) \right\rangle_{L^2(\Omega)},
\end{equation}
Where $f \cdot g$ denotes pointwise multiplication, and $f \ast g$ denotes convolution of the functions $f$ and $g$. Here
\begin{itemize}
	\item $\varphi_{x_i}$ is given by formula \eqref{eq:convolution_kernel}, but with $x$ replaced by $x_i$.
	\item $\{x_i\}_{i=1}^r \subset \Omega$ is a collection of points scattered throughout the domain.
	\item The functions $w_i(x)$ are spatially varying weighting function that interpolate the convolution kernels $\varphi_{x_i}$.
\end{itemize}
\eqref{eq:product_convolution}

To take advantage of local translation invariance, we sample $\varphi_{x_i}$ at a collection of points $\{x_i\}_{i=1}^r \subset \Omega$, and patch together the local convolution operators $u \mapsto \varphi_{x_i} \ast u$ using smooth weighting functions $w_i(x)$. This yields a product-convolution approximation, $\widetilde{\mathcal{A}} \approx \mathcal{A}$, given by
\begin{equation*}
	\left(\widetilde{\mathcal{A}}u\right)(v) := \left\langle v, \sum_{i=1}^r \varphi_{x_i} \ast \left(w_i \cdot u\right) \right\rangle_{L^2(\Omega)},
\end{equation*}
where $f \cdot g$ denotes pointwise multiplication of the functions $f$ and $g$. There is a long history of product-convolution operator approximation of this form; for a review of the literature,

@@

 $\left(\mathcal{A}u\right)(v) = \left\langle v, \varphi_p \ast u\right\rangle_{L^2(\Omega)}$. Here $f \ast g$ denotes convolution of the functions $f$ and $g$, and the convolution kernel,
